SIR Model With Testing Flows and Isolation

### 2020-12-08 codes/sir_macpan.Rnw
macpan/SIR equivalence

<<Try MacPan to recover the SIR result, echo=FALSE>>=
# update MacPan's params according to the SIR params
params <- update(params, c(beta0=sir.params[["beta"]],
                           alpha=0, ## no asymptomatic
                           sigma=3, ## very short latent period
                           gamma_a=sir.params[["gamma"]],
                           gamma_m=sir.params[["gamma"]],
                           gamma_s=sir.params[["gamma"]],
                           gamma_p=sir.params[["gamma"]]))

@@

gg01 <- (ggplot(sim_combined,aes(x=date))
+ geom_point(aes(y=I))
+ geom_point(aes(y=sir.I), color='red')
)
print(gg01)
print(gg01 + scale_y_log10())
@

>>>>

<<Try MacPan to recover the SIR result, echo=FALSE>>=
## update MacPan's params according to the SIR params
##
big_rate <- 20
params <- update(params, c(beta0=sir.params[["beta"]],
                           alpha=0, ## no asymptomatic
                           sigma=big_rate, ## very short latent period
                           ## would like this to -> Inf but can't
                           gamma_a=0,
                           mu=1,  ## all cases mild
                           gamma_m=sir.params[["gamma"]],
                           gamma_s=0,
                           ## try to skip presymptomatic period
                           gamma_p=big_rate
                           ))

@@

gg01 <- (ggplot(sim_combined,aes(x=date))
+ geom_point(aes(y=I))
+ geom_lines(aes(y=sir.I), color='red')
)
print(gg01)
print(gg01 + scale_y_log10())
@
